Metrics

### 2023-12-05 src/metrics.Rmd
Calc metrics by age range

# Bulk calc per model based on age, physician coding stage, and cause of death
calc_by <- function(
        df,
        func,
        name = "Metric",
        by_age = TRUE,
        by_stage = TRUE,
        by_cod = TRUE,
        ...
    ) {
    out <- list()

@@

                # Filter data for stage within age group
                df_filter <- df %>% filter(
                    .[[stage]] == TRUE & age == age_group
                )
                metric_name = paste0(
                    name,
                    " ",
                    str_to_title(age_group),
                    " ",
                    str_replace_all(stage, stage_format)
                )

@@

            # Filter data for cod
            df_filter <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE)
            metric_name = paste0(name, " COD Agree ", cod)

@@

>>>>

# Bulk calc per model based on age, physician coding stage, and cause of death
calc_by <- function(
        df,
        func,
        name = "Metric",
        by_age = TRUE,
        by_stage = TRUE,
        by_cod = TRUE,
        by_age_range = TRUE,
        ...
    ) {
    out <- list()

@@

                # Filter data for stage within age group
                df_filter <- df %>% filter(
                    .[[stage]] == TRUE & age == age_group
                )
                metric_name <- paste0(
                    name,
                    " ",
                    str_to_title(age_group),
                    " ",
                    str_replace_all(stage, stage_format)
                )

@@

            # Filter data for cod
            df_filter <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE)
            metric_name <- paste0(name, " COD Agree ", cod)

    # Calc metric by age range
    if (by_age_range) {

        # Get unique age ranges
        age_ranges <- df %>%
            pull(age_range) %>%
            unique

        # Calc metric by age range
        for (ar in age_ranges) {

            # Filter for age range
            df_filter <- df %>% filter(age_range == ar & is_agreed == TRUE)
            metric_name = paste0(name, " Age Agree ", ar)

@@

### Age Range Performance

Display a plot of performance for physician agreed records by age ranges.

# Get unique age range columns
arange_col <- out %>% select(starts_with("PCCC Age Agree ")) %>% names

# Create age range with counts
arange_remap <- list()
arange_counts <- list()
for (ar_col in arange_col) {

    # Get cod without prefix
    ar <- gsub("PCCC Age Agree ", "", ar_col)

    # Calculate num and perc cases for age range
    narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
    parange <- (narange / nagree) * 100
    parange_label <- if (round(parange) >= 1) round(parange) else "<1"

    # Break age range into newlines if more than 3 words
    if (str_count(ar, "\\s+") > 3) {
        arange_label <- str_replace(ar, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n")
    } else {
        arange_label <- ar
    }

    # Add label for cod
    arange_remap[[ar]] <- paste0(arange_label, "\n(n=", narange, ", ", parange_label, "%)")

    # Store cod count data
    arange_counts[[ar]] <- narange
}

# Prepare boxplot data
ardata <- out %>%
    select(
        Model,
        starts_with("PCCC COD Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC COD Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "COD",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "COD" = recode(`COD`, !!!cod_remap)
    ) %>%
    group_by(`COD`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
    )

# Create cod order based on max pccc
arorder <- ardata %>%
    group_by(COD) %>%
    summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
    select(COD, `PCCC Max Value`) %>%
    arrange(desc(`PCCC Max Value`)) %>%
    pull(COD)
coddata$COD <- factor(coddata$COD, levels = rev(codorder))
